\documentclass[11pt]{report}

% --- Packages ---
\usepackage[usenames, dvipsnames]{color} % Cool colors
\usepackage{enumerate, amsmath, amsthm, amssymb, algorithm, algpseudocode, pifont, subfig, fullpage, csquotes, dashrule, tikz, bbm, booktabs, bm, verbatim, url}
\usepackage[framemethod=TikZ]{mdframed}
\usepackage[numbers]{natbib}
\usepackage{hyperref}

% --- Misc. ---
\hbadness=10000 % No "underfull hbox" messages.
\setlength{\parindent}{0pt} % Removes all indentation.

% --- Commands ---
\input{commands}

% --- Meta Info ---
\title{deeplearning.ai Coursera Notes \thanks{\url{https://www.coursera.org/specializations/deep-learning}}}
\author{Daniel Ong\\ danielong1@gmail.com}
\date{March 2018}

% --- Begin Document ---
\begin{document}
\maketitle

\tableofcontents

\chapter*{About} 
\addcontentsline{toc}{chapter}{About}
This is my personal notes from all 5 courses of the Deep Learning specialization on Coursera by deeplearning.ai. The primary motivations for creating this document are to create a useful reference for myself and to solidify my understanding of concepts and algorithms. Chapters and sections generally correspond to courses and weeks in the Coursera sequence but I split weeks that contain multiple topics into separate sections.


\chapter{Neural Networks and Deep Learning}
\section*{Learning Objectives}
\begin{itemize}
  \item Understand fundamentals of neural networks
  \item Build a deep neural network that recognizes cats
\end{itemize}

\section{Introduction to Deep Learning}
Andrew Ng believes that the impact of artificial intelligence (AI) on society will be on the same magnitude as the impact of electricity on society a hundred years ago. Deep learning (DL) is the field of AI that has been improving rapidly and driving recent progress. DL is already a powerful and proven method for solving certain types of problems (e.g. advertising, image classification, etc). 


\section{Neural Network Basics}
Neural networks are very loosely based on neurons are connected in brains. In brains, special cells called neurons are connected to each other. 
\ddef{Artificial Neuron}{blah}
\ddef{Neural Network}{A neural network is a collection of nodes that apply an activation function onto input...}
\section{Shallow Neural Network}
\ddef{Shallow Neural Network}{A neural network is a collection of nodes that apply an activation function onto input...}
\section{Deep Neural Network}
\ddef{Deep Neural Network}{A neural network is a collection of nodes that apply an activation function onto input...}
\ddef{Deep Learning}{Deep Learning refers to the training of large neural networks.}

\chapter{Improving Deep Neural Networks}
\section{Practical Aspects of Deep Learning}
\section{Optimization Algorithms}
\section{Hyperparameter Tuning}
\section{Batch Normalization}
\section{Programming Frameworks}


\chapter{Structuring Machine Learning Projects}


\chapter{Convolutional Neural Networks}


\chapter{Sequence Models}



% --- Bibliography ---
\bibliographystyle{plainnat}
\bibliography{research}

\end{document}